\vspace{1.0cm} \Large \bf Integrating influenza antigenic dynamics with molecular evolution

### 2013-12-09 correspondence/reresponse.tex
Fix #36 - Ne*tau estimates.
Small update to issue #33.

\textbf{We appreciate this suggestion.  Including the biological explanation for why we observe virus effects in the form of decreased or increased overall HI reactivity is very important.  We've revised this section to put virus avidity at the forefront and relabeled `virus effects' to `virus avidities'.  This has the additional benefit of being more transparent of a term than the opaque `effect.'}

@@

>>>>

\textbf{We appreciate this suggestion.  Including the biological explanation for why we observe virus effects in the form of decreased or increased overall HI reactivity is very important.  We've revised this section to include references to virus avidity and relabeled `virus effects' to `virus avidities'.  This has the additional benefit of being more transparent of a term than the opaque `effect.'}

@@

\textbf{Thank you for catching this.  Estimates of $N_e\tau$ had been included in figure 4, but were moved to table 2 and the figure 4 legend not updated accordingly.  This has been fixed to leave just the estimates in table 2.}
